\verb+state_type+ & depth-first cursor & The type of the states
handles of the underlying DFA. \\ \hline
\verb+char_type+ & depth-first cursor & The type of the transitions
letters. \\ \hline 
\verb+tag_type+ & depth-first cursor & The type of the tags associated to
states. \\ \hline 
\verb+dfirst_cursor()+ & depth-first cursor & Construct a cursor with an
empty stack useful as end-of-range iterator. \\ \hline
\verb+dfirst_cursor(+ \verb+      const dfirst_cursor &c)+ &  depth-first cursor &
Copy constructor. \\ \hline 
\verb+state_type src() const+ & depth-first cursor & Return the state
handle the cursor is pointing to. \\ \hline
\verb+bool src_final() const+ & depth-first cursor & Return
\verb+true+ if the pointed state is final. \\ \hline
\verb+char_type letter() const+ & depth-first cursor & Return the
letter on the pointed transition. \\ \hline
\verb+bool aim() const+ & depth-first cursor & Return the handle of
the aim state the cursor is pointing to. \\ \hline
\verb+bool aim_final() const+  & depth-first cursor & Return
\verb+true+ if the aim state is final. \\ \hline
\verb+bool operator==(+ 
\verb+ const dfirst_cursor &c) const+ & depth-first cursor & Return
\verb+true+ iff both stacks are equal. \\ \hline
\verb+bool forward()+ & depth-first cursor & Increment the cursor
making it point to the next transition in the sequence. Return
\verb+true+ if the transition reached has been pushed onto the
stack. \\ \hline 
\verb+Tag src_tag() const+ & depth-first cursor & Return the tag
associated to the source state. \\ \hline
\verb+Tag aim_tag() const+ & depth-first cursor & Return the tag
associated to the aim state. \\ \hline
